### 2018-08-08 UnintentionalStateConflict/paper3/sections/Formalization.tex
Theorem 4 finished

\section{Proof}
\subsection{Properties}
\begin{theorem}[Subject Reduction]~\label{theorem_subject}
If $\judgeewf \Gamma {e : I}$ and $\mu | e \rightarrow \mu' | e'$, 
then $\judgeewf \Gamma {e' : I}$.
\end{theorem}
\begin{proof} ~\\
\indent \textbf{Case E-Invk.} Let
  $$e = (J)o.m(\overline{v}) \quad \judgeewf {\Gamma} {e : I_e}$$
  $$e' = (I_{e_0})[\overline{(I_x)v}/\overline{x}, (I_0)o/\kwthis]e_0$$
  $$\mbody(m, I, J) = (I_0, \overline{I_x} \; \overline{x}, I_{e_0} \; e_0)$$

@@

	\item \item If the last rule used in the derivation of $\mu \mid t \to \mu' \mid t'$ is \textsc{(E-CTX)}, 
\end{itemize}
\end{proof}

\subsubsection{Proof for Theorem~\ref{theorem_subject}}

\subsubsection{Proof for Theorem~\ref{theorem_progress}}

\subsubsection{Proof for Theorem~\ref{theorem_determinacy}}

>>>>

\section{Proof}
\subsection{Properties}

\begin{theorem}[Subject Reduction]~\label{theorem_subject}
If $\judgeewf \Gamma {e : I}$ and $\mu | e \rightarrow \mu' | e'$, 
then $\judgeewf \Gamma {e' : I}$.
\end{theorem}
\begin{proof} ~\\
\indent \textbf{Case E-Invk.} Let
  $$e = (J)o.m(\overline{v}) \quad \judgeewf {\Gamma} {e : I_e}$$
  $$e' = (I_{e_0})[\overline{(I_x)v}/\overline{x}, (I_0)o/\kwthis]e_0$$
  $$\mbody(m, I, J) = (I_0, \overline{I_x} \; \overline{x}, I_{e_0} \; e_0)$$

@@

    \item If the last rule used in the derivation of $\mu \mid t \to \mu' \mid t'$ is \textsc{(E-CTX)}, then there are 5 cases ($t$ could take 5 forms):
    \begin{itemize}
    	\item If $t = \mylet{I}{x}{\varepsilon}{e}$ and the precondition is $\mu \mid e \to \mu' \mid e'$. Then $t' = \varepsilon\{e'\}$ .Then for the second reduction $\mu \mid t \to \mu'' \mid t''$, the rule \textsc{(E-Let)} does not apply because $\varepsilon$ is reducible and does not conform to the form of $\mylet{I}{x}{o}{e}$ in \textsc{(E-Let)}. Thus the only rule applies is the rule \textsc{(E-CTX)}. Assume the precondition is $\mu \mid e \to \mu'' \mid e''$. By the induction hypothesis, $\mu'' = \mu'$ and $e'' = e'$. Therefore, $t'' = \varepsilon\{e''\} = \varepsilon\{e'\} = t'$. Proved.
    	\item The proof for the other cases, where 
    		$t = \varepsilon.m(\overline{e}) $, 
            $t = (J)o.m(\overline{o}, \varepsilon, \overline{e}) $
            $t = \newI{I}{\overline{o}, \varepsilon, \overline{e}} $
            or $t = (I)\varepsilon $ takes the same approach as the first case.
    \end{itemize}
\end{itemize}
\end{proof}
